Active Learning for SAT-Solver Benchmarking

### 2022-09-26 paper/paper.tex
Add license and orcid
Conduct minor adaptations to template
... based on the LNCS template's instructions and sample file:

- add font encoding
- avoid re-defining basic layout settings
- color links in blue
- add keywords
- use dedicated environment for definition (though we only have one)
- don't end captions with period if not full sentences

\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage[labelfont=bf]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage[table]{xcolor}
\usepackage{tikz}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{pifont}
\usepackage{tablefootnote}
\usepackage{array}
\usepackage[misc]{ifsym} % letter symbol to mark corresponding author

@@

\renewcommand{\arraystretch}{1.5}
%\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\setlength{\textfloatsep}{12pt}

\usepackage[ruled,vlined,linesnumbered,norelsize]{algorithm2e}
\DontPrintSemicolon
\def\NlSty#1{\textnormal{\fontsize{8}{10}\selectfont{}#1}}
\SetKwSty{texttt}
\SetCommentSty{emph}
\def\listalgorithmcfname{List of Algorithms}
\def\algorithmautorefname{Algorithm}
\let\chapter=\section % repariert ein Problem mit algorithm2e

@@

\author{
	Tobias Fuchs (\Letter) \and
	Jakob Bach\orcidID{0000-0003-0301-2798} \and
	Markus Iser\orcidID{0000-0003-2904-232X}
}

@@

\begin{abstract}
  Experimentation is one of the main phases in algorithm engineering, including the archetypal $\mathcal{NP}$-complete propositional-sat\-is\-fia\-bi\-li\-ty problem (SAT).
  While the field of SAT-solver benchmarking is well established, traditional benchmark-set-selection approaches do not optimize for benchmark runtime.
  Benchmark-set selection is the process of choosing a subset of instances out of a pool to be representative and reliable in discriminating SAT solvers.
  This paper presents an active-learning-based benchmark-set-selection approach that solves the new-solver problem:
  Given a new solver, we want to find its ranking amidst its competitors with as little runtime as possible while still giving accurate ranking predictions.
  To do so, we use well-known techniques from the domain of active learning.
  We can determine a new solver's rank regarding the SAT Competition 2022 Anniversary Track instances in about \SI{10}{\%} of the time it would take to run the solver on all instances of this dataset.
  We achieve this while still maintaining a prediction accuracy of about \SI{92}{\%} regarding the PAR-2 ranking of this solver if it were evaluated on the complete dataset.
  Instance-selection decisions made by our approach also allow for discussing instance-family importance in the selection process. 
  Our tool provides the engineer of propositional-satisfiability solvers with a faster way of determining a new SAT-solver's performance in comparison to sampling the benchmark set by hand.
\end{abstract}

@@

\textbf{New solver problem.} Given a pool of instances $\mathcal{I}$ and solvers $\mathcal{A}$ with already known runtimes $r\!: \mathcal{A} \times \mathcal{I} \rightarrow \left[0, \tau\right] \cup \left\lbrace \perp \right\rbrace$ (timeout $\tau$ usually \SI{5000}{s}~\cite{FroleyksHIJS21}), the problem is to decide with as little resources (CPU time) as possible how a new solver $\hat{a} \notin \mathcal{A}$ performs in comparison to the existing ones by incrementally selecting a benchmark set $\tilde{\mathcal{I}}$ on which to evaluate $\hat{a}$.
We want to find a scoring function $\operatorname{score}\!: \mathcal{A} \cup \left\lbrace \hat{a} \right\rbrace \rightarrow \mathbb{R}$ assigning each solver a score.
Having a set of solvers with their respective scores induces a ranking.
This allows for both comparing the solvers as well as identifying solvers with similar behavior.
While the annual SAT~Competitions~\cite{FroleyksHIJS21} rely on the PAR-2 score ranking, i.e, the average runtime with a penalty timeout-term of $2\tau$, which we want to predict, this work examines a model-based way of ranking solvers.

@@

\begin{table}[tbp]
  \centering
  \caption{Support for desired features that are introduced in Sec.~\ref{sec:intro}. The shown approaches include traditional benchmark-set-selection techniques~\cite{HoosKSS13}, an algorithm configuration system~\cite{HutterHL11}, an existing active-learning approach~\cite{MatriconAFSH21}, as well as our approach.}
  \label{tab:requirements}
  \vspace{0.2cm}
  \begin{tabular}{
    m{0.2\textwidth}
    >{\centering\arraybackslash}m{0.15\textwidth}
    >{\centering\arraybackslash}m{0.15\textwidth}
    >{\centering\arraybackslash}m{0.15\textwidth}
    >{\centering\arraybackslash}m{0.15\textwidth}
  }
    \hline
    Feature & Hoos \mbox{et. al.~\cite{HoosKSS13}} & SMAC~\cite{HutterHL11} & Matricon \mbox{et. al.~\cite{MatriconAFSH21}} & Our approach \\
    \hline
    Ranking & \cmark & \xmark & \cmark & \cmark \\
    Runtime \mbox{optimization} & \xmark & \cmark & \cmark & \cmark \\
    %Feature-based & \cmark & \cmark & \cmark & \cmark \\
    Incremental \mbox{non-random} \mbox{sampling} & \xmark & \xmark & \cmark & \cmark \\
    % \tablefootnote{While using a model-based selection strategy to select the next configuration to evaluate, the instance sampling is done randomly.}
    Interpretability & \cmark & \xmark & \xmark & \cmark \\
    % \tablefootnote{While they provide a confidence measure, the strategy's output is still only binary, i.e., whether a solver A is better or worse than solver B.}
    Scalability & \cmark & \cmark & \xmark & \cmark \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{figure}[tbp!]
  \centering
  \begin{tabular}[c]{ccc}
  \begin{subfigure}[b]{0.26\textwidth}
  \centering
  \resizebox{!}{2.85cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Approx. Function};
  \node at (-2.8,0.25) {$f$};
  \end{tikzpicture}
  }
  \caption{Passive.}
  \label{fig:passive}
  \end{subfigure}
  &
  \begin{subfigure}[b]{0.36\textwidth}
  \centering
  \resizebox{!}{2.85cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Approx. Function};
  \node at (-2.8,0.25) {$f$};
  \node[right] at (-1.2,2.4) {Pool};
  \draw[->, densely dashed] (-2.4,1.2) arc (-90:0:0.8);
  \draw[->, densely dashed] (-1.6,2.8) arc (0:90:0.8);
  \node[right] at (-1.6,3.135) {$x, ?$};
  \draw  (-1.6,2.4) ellipse (0.4 and 0.3);
  \draw[fill=black]  (-1.725,2.5) ellipse (0.07 and 0.07);
  \draw[fill=black]  (-1.625,2.25) ellipse (0.07 and 0.07);
  \draw[fill=black]  (-1.425,2.4) ellipse (0.07 and 0.07);
  \end{tikzpicture}
  }
  \caption{Active Pool-based.}
  \label{fig:activepool}
  \end{subfigure}
  &
  \begin{subfigure}[b]{0.36\textwidth}
  \centering
  \resizebox{!}{2.85cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Approx. Function};
  \node at (-2.8,0.25) {$f$};
  \node[right] at (-1.1,2.4) {GAN};
  \node[right] at (-1.3,3.135) {$x, ?$};
  \draw[->, densely dashed] (-2.4,1.2) arc (-90:90:1.2);
  \end{tikzpicture}
  }
  \caption{Active Synthesis-based.}
  \label{fig:activesynth}
  \end{subfigure}
  \end{tabular}

  \caption{Types of Learning (depiction inspired by Rubens~et.al.~\cite{RubensESK15}).}
  \label{fig:learning}
\end{figure}

@@

\begin{algorithm}
  \caption{Simple incremental benchmark-set-selection schema.}
  \label{algALBenchmark}

@@

\begin{table}[tbp]
  \centering
  \caption{PAR-2 ranking vs. ranking based on discretized runtimes for the SAT Competition~2022 Anniversary Track instances~\cite{sat2022} ($k = 3$; hierarchical clustering).}
  \label{tab:discreteranking}
  \vspace{0.2cm}
  \begin{tabular}{
    c
    >{\centering\arraybackslash}p{2.2cm}p{3.6cm}
    >{\centering\arraybackslash}p{1.8cm}p{3.3cm}
  }
    \hline
    Rank & \multicolumn{2}{c}{PAR-2 Ranking} & \multicolumn{2}{c}{Cluster-Label Ranking} \\
    \hline
1   & 2806.400 & Kissat\_MAB\_ESA           & 1.172 & Kissat\_MAB\_ESA \\
2   & 2810.959 & kissat-sc2022-bulky        & 1.183 & kissat-sc2022-bulky \\
3   & 2830.143 & ekissat-mab-gb-db          & 1.185 & ekissat-mab-gb-db \\
\cellcolor{gray!15} 4   & \cellcolor{gray!15} 2833.081 & \cellcolor{gray!15} Kissat\_MAB\_UCB           & \cellcolor{gray!15} 1.186 & \cellcolor{gray!15} kissat\_inc \\
\cellcolor{gray!15} 5   & \cellcolor{gray!15} 2833.397 & \cellcolor{gray!15} kissat\_inc                & \cellcolor{gray!15} 1.186 & \cellcolor{gray!15} Kissat\_MAB\_UCB \\
6   & 2841.734 & ekissat-mab-db-v1          & 1.192 & ekissat-mab-db-v1 \\
7   & 2842.666 & Kissat\_MAB\_MOSS          & 1.192 & Kissat\_MAB\_MOSS \\
8   & 2857.219 & Kissat\_MAB-HyWalk         & 1.195 & Kissat\_MAB-HyWalk \\
9   & 2866.960 & kissat-sc2022-light        & 1.120 & kissat-sc2022-light \\
10  & 2896.371 & kissat-els-v2              & 1.216 & kissat-els-v2 \\
11  & 2950.179 & hKis-unsat                 & 1.229 & hKis-unsat \\
12  & 2964.729 & Kissat\_adaptive\_restart  & 1.234 & Kissat\_adaptive\_restart \\
13  & 2974.990 & SeqFROST-NoExtend          & 1.247 & SeqFROST-NoExtend \\
14  & 3010.642 & Cadical\_ESA               & 1.248 & Cadical\_ESA \\
\cellcolor{gray!15} 15  & \cellcolor{gray!15} 3012.152 & \cellcolor{gray!15} kissat-els-v1              & \cellcolor{gray!15} 1.258 & \cellcolor{gray!15} CadicalReorder \\
\cellcolor{gray!15} 16  & \cellcolor{gray!15} 3028.922 & \cellcolor{gray!15} CadicalReorder             & \cellcolor{gray!15} 1.264 & \cellcolor{gray!15} kissat-els-v1 \\
\cellcolor{gray!15} 17  & \cellcolor{gray!15} 3042.540 & \cellcolor{gray!15} cadical\_rel\_Scavel       & \cellcolor{gray!15} 1.278 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V1 \\
\cellcolor{gray!15} 18  & \cellcolor{gray!15} 3082.293 & \cellcolor{gray!15} kissat\_relaxed            & \cellcolor{gray!15} 1.283 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V2 \\
\cellcolor{gray!15} 19  & \cellcolor{gray!15} 3089.304 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V1          & \cellcolor{gray!15} 1.298 & \cellcolor{gray!15} kissat\_relaxed \\
\cellcolor{gray!15} 20  & \cellcolor{gray!15} 3095.118 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V2          & \cellcolor{gray!15} 1.361 & \cellcolor{gray!15} cadical\_rel\_Scavel \\
21  & 3272.674 & glucose-reboot             & 1.379 & glucose-reboot \\
\cellcolor{gray!15} 22  & \cellcolor{gray!15} 3287.322 & \cellcolor{gray!15} LStech-Maple-HyWalk        & \cellcolor{gray!15} 1.414 & \cellcolor{gray!15} hCaD\_V1-psids \\
23  & 3288.798 & LSTech\_Maple              & 1.446 & LSTech\_Maple \\
\cellcolor{gray!15} 24  & \cellcolor{gray!15} 3399.281 & \cellcolor{gray!15} SLIME-SC-2022-beta         & \cellcolor{gray!15} 1.469 & \cellcolor{gray!15} LStech-Maple-HyWalk \\
\cellcolor{gray!15} 25  & \cellcolor{gray!15} 3410.345 & \cellcolor{gray!15} SLIME-SC-2022              & \cellcolor{gray!15} 1.470 & \cellcolor{gray!15} SLIME-SC-2022-beta \\
\cellcolor{gray!15} 26  & \cellcolor{gray!15} 3430.403 & \cellcolor{gray!15} hCaD\_V1-psids             & \cellcolor{gray!15} 1.523 & \cellcolor{gray!15} SLIME-SC-2022 \\
27  & 3504.244 & MapleLCMDistChrBt-DL-v3    & 1.542 & MapleLCMDistChrBt-DL-v3 \\
28  & 4750.808 & IsaSAT                     & 2.062 & IsaSAT \\
    \hline
  \end{tabular}
\end{table}

@@

\vspace{-0.2cm}
\begin{algorithm}[htbp]
  \caption{Evaluation framework.}
  \label{alg:eval}

@@

  \caption{$O_{\operatorname{rt}}$-$O_{\operatorname{acc}}$-diagrams showing the performance of different hyper-parameter instantiations. The x-axis shows the fraction of runtime in comparison to the time needed to evaluate a solver on all instances. The y-axis shows the accuracy of the predicted rank in comparison to the true PAR-2 rank. Each line entails the front of Pareto-optimal configurations with the respective instantiation.}
  \label{fig:e2eallsolvers}
\end{figure}

>>>>

\usepackage[T1]{fontenc} % recommended by LNCS template
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage[labelfont=bf]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage[table]{xcolor}
\usepackage{tikz}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{pifont}
\usepackage{tablefootnote}
\usepackage{array}
\usepackage[misc]{ifsym} % letter symbol to mark corresponding author

@@

\usepackage[ruled,vlined,linesnumbered,norelsize]{algorithm2e}
\DontPrintSemicolon
\def\NlSty#1{\textnormal{\fontsize{8}{10}\selectfont{}#1}}
\SetKwSty{texttt}
\SetCommentSty{emph}

\renewcommand\UrlFont{\color{blue}\rmfamily} % link coloring according to LNCS template

@@

\author{
	Tobias Fuchs\orcidID{0000-0001-9727-2878} (\Letter) \and \\
	Jakob Bach\orcidID{0000-0003-0301-2798} \and \\
	Markus Iser\orcidID{0000-0003-2904-232X}
}

@@

\begin{abstract}
  Experimentation is one of the main phases in algorithm engineering, including the archetypal $\mathcal{NP}$-complete propositional-sat\-is\-fia\-bi\-li\-ty problem (SAT).
  While the field of SAT-solver benchmarking is well established, traditional benchmark-set-selection approaches do not optimize for benchmark runtime.
  Benchmark-set selection is the process of choosing a subset of instances out of a pool to be representative and reliable in discriminating SAT solvers.
  This paper presents an active-learning-based benchmark-set-selection approach that solves the new-solver problem:
  Given a new solver, we want to find its ranking amidst its competitors with as little runtime as possible while still giving accurate ranking predictions.
  To do so, we use well-known techniques from the domain of active learning.
  We can determine a new solver's rank regarding the SAT Competition 2022 Anniversary Track instances in about \SI{10}{\%} of the time it would take to run the solver on all instances of this dataset.
  We achieve this while still maintaining a prediction accuracy of about \SI{92}{\%} regarding the PAR-2 ranking of this solver if it were evaluated on the complete dataset.
  Instance-selection decisions made by our approach also allow for discussing instance-family importance in the selection process. 
  Our tool provides the engineer of propositional-satisfiability solvers with a faster way of determining a new SAT-solver's performance in comparison to sampling the benchmark set by hand.

  \keywords{Propositional satisfiability \and Benchmarking \and Active learning}
\end{abstract}

@@

\begin{definition}[New solver problem]
	Given a pool of instances $\mathcal{I}$ and solvers $\mathcal{A}$ with already known runtimes $r\!: \mathcal{A} \times \mathcal{I} \rightarrow \left[0, \tau\right] \cup \left\lbrace \perp \right\rbrace$ (timeout $\tau$ usually \SI{5000}{s}~\cite{FroleyksHIJS21}), the problem is to decide with as little resources (CPU time) as possible how a new solver $\hat{a} \notin \mathcal{A}$ performs in comparison to the existing ones by incrementally selecting a benchmark set $\tilde{\mathcal{I}}$ on which to evaluate $\hat{a}$.
\end{definition}

We want to find a scoring function $\operatorname{score}\!: \mathcal{A} \cup \left\lbrace \hat{a} \right\rbrace \rightarrow \mathbb{R}$ assigning each solver a score.
Having a set of solvers with their respective scores induces a ranking.
This allows for both comparing the solvers as well as identifying solvers with similar behavior.
While the annual SAT~Competitions~\cite{FroleyksHIJS21} rely on the PAR-2 score ranking, i.e, the average runtime with a penalty timeout-term of $2\tau$, which we want to predict, this work examines a model-based way of ranking solvers.

@@

\begin{table}[tbp]
  \centering
  \caption{Support for desired features that are introduced in Sec.~\ref{sec:intro}. The shown approaches include traditional benchmark-set-selection techniques~\cite{HoosKSS13}, an algorithm configuration system~\cite{HutterHL11}, an existing active-learning approach~\cite{MatriconAFSH21}, as well as our approach.}
  \label{tab:requirements}
  \vspace{0.2cm}
  \begin{tabular}{
    m{0.3\textwidth}
    >{\centering\arraybackslash}m{0.15\textwidth}
    >{\centering\arraybackslash}m{0.15\textwidth}
    >{\centering\arraybackslash}m{0.15\textwidth}
    >{\centering\arraybackslash}m{0.15\textwidth}
  }
    \hline
    Feature & Hoos \mbox{et. al.~\cite{HoosKSS13}} & SMAC~\cite{HutterHL11} & Matricon \mbox{et. al.~\cite{MatriconAFSH21}} & Our approach \\
    \hline
    Ranking & \cmark & \xmark & \cmark & \cmark \\
    Runtime optimization & \xmark & \cmark & \cmark & \cmark \\
    %Feature-based & \cmark & \cmark & \cmark & \cmark \\
    Incremental non-random sampling & \xmark & \xmark & \cmark & \cmark \\
    % \tablefootnote{While using a model-based selection strategy to select the next configuration to evaluate, the instance sampling is done randomly.}
    Interpretability & \cmark & \xmark & \xmark & \cmark \\
    % \tablefootnote{While they provide a confidence measure, the strategy's output is still only binary, i.e., whether a solver A is better or worse than solver B.}
    Scalability & \cmark & \cmark & \xmark & \cmark \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{figure}[tbp!]
  \centering
  \begin{tabular}[c]{ccc}
  \begin{subfigure}[b]{0.26\textwidth}
  \centering
  \resizebox{!}{2.85cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Approx. Function};
  \node at (-2.8,0.25) {$f$};
  \end{tikzpicture}
  }
  \caption{Passive}
  \label{fig:passive}
  \end{subfigure}
  &
  \begin{subfigure}[b]{0.36\textwidth}
  \centering
  \resizebox{!}{2.85cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Approx. Function};
  \node at (-2.8,0.25) {$f$};
  \node[right] at (-1.2,2.4) {Pool};
  \draw[->, densely dashed] (-2.4,1.2) arc (-90:0:0.8);
  \draw[->, densely dashed] (-1.6,2.8) arc (0:90:0.8);
  \node[right] at (-1.6,3.135) {$x, ?$};
  \draw  (-1.6,2.4) ellipse (0.4 and 0.3);
  \draw[fill=black]  (-1.725,2.5) ellipse (0.07 and 0.07);
  \draw[fill=black]  (-1.625,2.25) ellipse (0.07 and 0.07);
  \draw[fill=black]  (-1.425,2.4) ellipse (0.07 and 0.07);
  \end{tikzpicture}
  }
  \caption{Active Pool-based}
  \label{fig:activepool}
  \end{subfigure}
  &
  \begin{subfigure}[b]{0.36\textwidth}
  \centering
  \resizebox{!}{2.85cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Approx. Function};
  \node at (-2.8,0.25) {$f$};
  \node[right] at (-1.1,2.4) {GAN};
  \node[right] at (-1.3,3.135) {$x, ?$};
  \draw[->, densely dashed] (-2.4,1.2) arc (-90:90:1.2);
  \end{tikzpicture}
  }
  \caption{Active Synthesis-based}
  \label{fig:activesynth}
  \end{subfigure}
  \end{tabular}

  \caption{Types of Learning (depiction inspired by Rubens~et.al.~\cite{RubensESK15})}
  %JB: slightly larger font size in figure (at least having the size of the caption) would be nice
  \label{fig:learning}
\end{figure}

@@

\begin{algorithm}
  \caption{Simple incremental benchmark-set-selection schema}
  \label{algALBenchmark}

@@

\begin{table}[tbp]
  \centering
  \caption{PAR-2 ranking vs. ranking based on discretized runtimes for the SAT Competition~2022 Anniversary Track instances~\cite{sat2022} ($k = 3$; hierarchical clustering)}
  \label{tab:discreteranking}
  \vspace{0.2cm}
  \begin{tabular}{
    c
    >{\centering\arraybackslash}p{2.2cm}p{3.6cm}
    >{\centering\arraybackslash}p{1.8cm}p{3.3cm}
  }
    \hline
    Rank & \multicolumn{2}{c}{PAR-2 Ranking} & \multicolumn{2}{c}{Cluster-Label Ranking} \\
    \hline
1   & 2806.400 & Kissat\_MAB\_ESA           & 1.172 & Kissat\_MAB\_ESA \\
2   & 2810.959 & kissat-sc2022-bulky        & 1.183 & kissat-sc2022-bulky \\
3   & 2830.143 & ekissat-mab-gb-db          & 1.185 & ekissat-mab-gb-db \\
\cellcolor{gray!15} 4   & \cellcolor{gray!15} 2833.081 & \cellcolor{gray!15} Kissat\_MAB\_UCB           & \cellcolor{gray!15} 1.186 & \cellcolor{gray!15} kissat\_inc \\
\cellcolor{gray!15} 5   & \cellcolor{gray!15} 2833.397 & \cellcolor{gray!15} kissat\_inc                & \cellcolor{gray!15} 1.186 & \cellcolor{gray!15} Kissat\_MAB\_UCB \\
6   & 2841.734 & ekissat-mab-db-v1          & 1.192 & ekissat-mab-db-v1 \\
7   & 2842.666 & Kissat\_MAB\_MOSS          & 1.192 & Kissat\_MAB\_MOSS \\
8   & 2857.219 & Kissat\_MAB-HyWalk         & 1.195 & Kissat\_MAB-HyWalk \\
9   & 2866.960 & kissat-sc2022-light        & 1.120 & kissat-sc2022-light \\
10  & 2896.371 & kissat-els-v2              & 1.216 & kissat-els-v2 \\
11  & 2950.179 & hKis-unsat                 & 1.229 & hKis-unsat \\
12  & 2964.729 & Kissat\_adaptive\_restart  & 1.234 & Kissat\_adaptive\_restart \\
13  & 2974.990 & SeqFROST-NoExtend          & 1.247 & SeqFROST-NoExtend \\
14  & 3010.642 & Cadical\_ESA               & 1.248 & Cadical\_ESA \\
\cellcolor{gray!15} 15  & \cellcolor{gray!15} 3012.152 & \cellcolor{gray!15} kissat-els-v1              & \cellcolor{gray!15} 1.258 & \cellcolor{gray!15} CadicalReorder \\
\cellcolor{gray!15} 16  & \cellcolor{gray!15} 3028.922 & \cellcolor{gray!15} CadicalReorder             & \cellcolor{gray!15} 1.264 & \cellcolor{gray!15} kissat-els-v1 \\
\cellcolor{gray!15} 17  & \cellcolor{gray!15} 3042.540 & \cellcolor{gray!15} cadical\_rel\_Scavel       & \cellcolor{gray!15} 1.278 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V1 \\
\cellcolor{gray!15} 18  & \cellcolor{gray!15} 3082.293 & \cellcolor{gray!15} kissat\_relaxed            & \cellcolor{gray!15} 1.283 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V2 \\
\cellcolor{gray!15} 19  & \cellcolor{gray!15} 3089.304 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V1          & \cellcolor{gray!15} 1.298 & \cellcolor{gray!15} kissat\_relaxed \\
\cellcolor{gray!15} 20  & \cellcolor{gray!15} 3095.118 & \cellcolor{gray!15} CaDiCaL\_DVDL\_V2          & \cellcolor{gray!15} 1.361 & \cellcolor{gray!15} cadical\_rel\_Scavel \\
21  & 3272.674 & glucose-reboot             & 1.379 & glucose-reboot \\
\cellcolor{gray!15} 22  & \cellcolor{gray!15} 3287.322 & \cellcolor{gray!15} LStech-Maple-HyWalk        & \cellcolor{gray!15} 1.414 & \cellcolor{gray!15} hCaD\_V1-psids \\
23  & 3288.798 & LSTech\_Maple              & 1.446 & LSTech\_Maple \\
\cellcolor{gray!15} 24  & \cellcolor{gray!15} 3399.281 & \cellcolor{gray!15} SLIME-SC-2022-beta         & \cellcolor{gray!15} 1.469 & \cellcolor{gray!15} LStech-Maple-HyWalk \\
\cellcolor{gray!15} 25  & \cellcolor{gray!15} 3410.345 & \cellcolor{gray!15} SLIME-SC-2022              & \cellcolor{gray!15} 1.470 & \cellcolor{gray!15} SLIME-SC-2022-beta \\
\cellcolor{gray!15} 26  & \cellcolor{gray!15} 3430.403 & \cellcolor{gray!15} hCaD\_V1-psids             & \cellcolor{gray!15} 1.523 & \cellcolor{gray!15} SLIME-SC-2022 \\
27  & 3504.244 & MapleLCMDistChrBt-DL-v3    & 1.542 & MapleLCMDistChrBt-DL-v3 \\
28  & 4750.808 & IsaSAT                     & 2.062 & IsaSAT \\
    \hline
  \end{tabular}
\end{table}

@@

\vspace{-0.2cm}
\begin{algorithm}[htbp]
  \caption{Evaluation framework}
  \label{alg:eval}

@@

  \caption{$O_{\operatorname{rt}}$-$O_{\operatorname{acc}}$-diagrams showing the performance of different hyper-parameter instantiations. The x-axis shows the fraction of runtime in comparison to the time needed to evaluate a solver on all instances. The y-axis shows the accuracy of the predicted rank in comparison to the true PAR-2 rank. Each line entails the front of Pareto-optimal configurations with the respective instantiation.}
  %JB: not sure if the color palette in the plots is grayscale-/color-blind-friendly; consider changing the palette (see https://colorbrewer2.org/#type=qualitative&scheme=Set3&n=3 ) and using different line types
  \label{fig:e2eallsolvers}
\end{figure}
